The Weakly Nonlinear Magnetorotational Instability in a thin-gap Taylor Couette flow

### 2016-09-30 paper/thingap_mri_paper.tex
very short draft of conclusion section. need to add more here...

>>>>

\section{Conclusion}
\label{sec:conclusion}

In this paper, we have constructed a weakly nonlinear analysis of the MRI using multiple-scales analysis. We find that the saturated state is a complex balance in which reduction of shear and amplification and redistribution of $B_z$ combine to saturate the instability. We confirm the previous results of \citet{Umurhan:2007hs}, including their $A^2 \propto \Pm^{4/3} $ scaling.
